\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\nofiles
\pagestyle{empty}  

\setlist[enumerate]{itemsep=0mm}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{\color{blue}}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-3pt}}
  }
}

\newcommand{\resumeSingleSubItem}[1]{
   \item\small{#1} \vspace{-3pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\projectSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-10pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand{\name}[1]{
  \centerline{\huge \textbf{#1}}
  \vspace{1.25ex}
}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\name{SHENGJIA YAN}
\centerline{(+86)15961887272 \textperiodcentered\ \href{mailto:sjyan1995@gmail.com}{sjyan1995@gmail.com} \textperiodcentered\ yanshengjia.com \textperiodcentered\ https://github.com/yanshengjia}


%-----------EDUCATION-----------------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
        {\href{http://www.seu.edu.cn/}{Southeast University (SEU)}}{2013.08 - 2017.06}
        {B.E. in Computer Science;  GPA: 3.56/4.0}{Nanjing, China}
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Working Experience}
    \resumeSubHeadingListStart

    \resumeSubheading
        {\href{https://17zuoye.com}{17zuoye AI Research Group}}{2017.06 - Present}
        {NLP Engineer}{Beijing, China}
        \resumeItemListStart
            \resumeSingleSubItem{Led a team of six to design and develop an automated essay enhancing system}
            \resumeSingleSubItem{Built an automated essay score predictor based on Feature Engineering, Logistic Regression and LSTM, which reached best performance on Kaggle ASAP dataset.}
            \resumeSingleSubItem{Developed a grammar checker based on Convolutional Seq2Seq and rules, which reached best F0.5-score on CoNLL2014 dataset. Reduced deep learning inference time by 50\% by utilizing Nvidia TensorRT.}
        \resumeItemListEnd

    \resumeSubheading
        {Knowledge Science and Engineering Lab @ Southeast University}{2014.10 - 2017.06}
        {Research Assistant (advisor: Prof. \href{http://cse.seu.edu.cn/PersonalPage/qgl/index.htm}{Guilin Qi})}{Nanjing, China}
        \resumeItemListStart
            \resumeSingleSubItem
                {Conducted data preprocessing using NLP approaches like spaCy to refine and analyze datasets.}
            \resumeSingleSubItem
                {Presented and implemented a Random Walk algorithm in Python based on Probabilistic Graphical Model to map the string mentions in web tables to their referent entities in a knowledge base.}
            \resumeSingleSubItem
                {Achieved 6\% increase in F1-score compared with the state-of-the-art scheme. The result was \textbf{published in [1, 2]}.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{\href{https://yanshengjia.com/projects}{Selected Projects}}
    \resumeSubHeadingListStart
        \projectSubheading{Deep Learning Grammar Error Correction System}{2018.06}
          \resumeItemListStart
            \resumeSingleSubItem{Designed and developed a GEC system based on Facebook well-known Convolutional Seq2Seq paper and rule-based proofreading software LanguageTool.}
            \resumeSingleSubItem{Supported grammar checking of more than 1000 tokens per second on single Tesla P100 GPU by optimizing deep learning inference with Nvidia TensorRT and ONNX.}
          \resumeItemListEnd
            
        \projectSubheading{Crowdsourcing NLP Annotation Platform}{2018.05}
          \resumeItemListStart
            \resumeSingleSubItem{Designed a crowdsourcing annotation system with multiple quality control mechanisms based on annotation tool BRAT.}
            \resumeSingleSubItem{Developed the frontend with HTML, Bootstrap and Javascript.}
            \resumeSingleSubItem{Built the backend service using Tornado/Python, MongoDB and deployed on AWS.}
          \resumeItemListEnd

        \projectSubheading{DNN-Based Face Recognition System}{2017.03}
          \resumeItemListStart
            \resumeSingleSubItem{Implemented the neural network Backpropagation algorithm in C and Constructed a DNN to recognize human's face, pose and experssion.}
            \resumeSingleSubItem{145+ stars and 180+ forks on GitHub}
          \resumeItemListEnd

        \projectSubheading{C-Minus Compiler}{2016.06}
          \resumeItemListStart
            \resumeSingleSubItem{Implemented the Regular-Expression-to-NFA converter, LR(1) parser and semantic analysis module in Python.}
            \resumeSingleSubItem{Visualized the compiling process by ploting NFA, DFA, GOTO graphs with GraphViz.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------------
\section{Publications}
    \begin{enumerate}[leftmargin=*, itemsep=0pt]
        \resumeSingleSubItem{``Entity Linking in Web Tables with Multiple Linked Knowledge Bases'', In: \textit{Semantic Technology: 6th Joint International Conference: JIST 2017}. pp. 239-253 \href{https://link.springer.com/chapter/10.1007/978-3-319-50112-3_18}{[pdf]}}
        \resumeSingleSubItem{``A Method of Entity Linking in Web Tables based on Multiple Linked Knowledge Bases'', Chinese Patent, CN106503148A, 2017} 
    \end{enumerate}\vspace{-10pt}


%--------SKILLS------------
\section{Skills}
    \begin{itemize}[leftmargin=*, itemsep=0pt]
        \resumeSingleSubItem{Languages: Python, C/C++, JavaScript, Markdown, \LaTeX}
        \resumeSingleSubItem{Tools: Git, MongoDB, Tornado, Bootstrap, Qt}
        \resumeSingleSubItem{Frameworks: TensorFlow, PyTorch, Scikit-Learn, Gensim, spaCy}
    \end{itemize}\vspace{-10pt}

%--------Honors------------
\section{Honors}
    \begin{itemize}[leftmargin=*, itemsep=0pt]
        \resumeSingleSubItem{Computer Programming Contest (Jiangsu Province), Third Prize, 2016.11}
        \resumeSingleSubItem{SEU Computer Programming Contest, Fourth Place, 2016.10}
        \resumeSingleSubItem{Outstanding Project, SEU Student Research Training Program, 2016.05}
    \end{itemize}\vspace{-10pt}

%--------Extracurricular Activities------------
\section{Extracurricular Activities}
    \begin{itemize}[leftmargin=*, itemsep=0pt]
        \resumeSingleSubItem{International Student Leadership Program, California Polytechnic State University, CA, USA, 2016.01}
        \resumeSingleSubItem{Nanjing Youth Olympic Games Volunteers, National Olympic Committee Assistant, Nanjing, China, 2014.07}
    \end{itemize}\vspace{-10pt}


%-------------------------------------------
\end{document}
